Multispecies survey specifications

### 2020-10-23 msSurveysTest.Rmd
add true bio and catch comparisons

# plot biomass time series facet wrapped by species
plotB <- function(dat){

    ggplot() +
    geom_line(data=dat, aes(x=time/stepperyr,y=atoutput, color="Survey Biomass"), 
              alpha = 10/10) +
    theme_tufte() +
    theme(legend.position = "top") +
    xlab("model year") +
    ylab("tons") +
    labs(colour=scenario.name) +
    facet_wrap(~species, scales="free")

@@

# make a catch series function that can be split by fleet? this doesnt
# also note different time (days) from model timestep in all other output
plotC <- function(dat){

    ggplot() +
    geom_line(data=dat, aes(x=time/365,y=atoutput, color="Catch biomass"), 
              alpha = 10/10) +
    theme_tufte() +
    theme(legend.position = "top") +
    xlab("model year") +
    ylab("tons") +
    labs(colour=scenario.name) +
    facet_wrap(~species, scales="free")

@@

# plot length frequencies by timestep (one species)
plotlen <- function(dat){

@@

# plot numbers at age by timestep (one species)
Natageplot <- function(dat){
  ggplot(dat, aes(x=agecl, y=atoutput)) +
    geom_point() +
    theme_tufte() +
    xlab("age/agecl") +
    ylab("number") +
    labs(subtitle = paste(scenario.name,
                          dat$species)) + 
    facet_wrap(~time/stepperyr, ncol=6, scales="free_y")
}

# plot weight at age time series facet wrapped by species
wageplot <- function(dat){
  ggplot(dat, aes(time/stepperyr, atoutput)) +
    geom_line(aes(colour = factor(agecl))) +
    theme_tufte() +
    theme(legend.position = "bottom") +
    xlab("model year") +
    ylab("average individual weight (g)") +
    labs(subtitle = paste0(scenario.name)) +
    facet_wrap(c("species"), scales="free_y")
}

@@

for(s in names(survObsBiom)){
  cat("  \n##### ",  s,"  \n")
  print(plotB(survObsBiom[[s]][[1]]))
  cat("  \n")
}

@@

plotC(catchbio_ss)

>>>>

# plot biomass time series facet wrapped by species
plotB <- function(dat, truedat=NULL){

    ggplot() +
    geom_line(data=dat, aes(x=time/stepperyr,y=atoutput, color="Survey Biomass"), 
              alpha = 10/10) +
    {if(!is.null(truedat)) geom_line(data=truedat, aes(x=time/365,y=atoutput, color="True B"), alpha = 3/10)} + 
    theme_tufte() +
    theme(legend.position = "top") +
    xlab("model year") +
    ylab("tons") +
    labs(colour=scenario.name) +
    facet_wrap(~species, scales="free")

@@

# make a catch series function that can be split by fleet? this doesnt
# also note different time (days) from model timestep in all other output
plotC <- function(dat, truedat=NULL){

    ggplot() +
    geom_line(data=dat, aes(x=time/365,y=atoutput, color="Catch biomass"), 
              alpha = 10/10) +
    {if(!is.null(truedat)) geom_line(data=truedat, aes(x=time/365,y=atoutput, color="True Catch"), alpha = 3/10)} + 
    theme_tufte() +
    theme(legend.position = "top") +
    xlab("model year") +
    ylab("tons") +
    labs(colour=scenario.name) +
    facet_wrap(~species, scales="free")

@@

# plot length frequencies by timestep (one species)
plotlen <- function(dat, truedat=NULL){

@@

# plot numbers at age by timestep (one species)
Natageplot <- function(dat, truedat=NULL){
  ggplot(dat, aes(x=agecl, y=atoutput)) +
    geom_point() +
    theme_tufte() +
    xlab("age/agecl") +
    ylab("number") +
    labs(subtitle = paste(scenario.name,
                          dat$species)) + 
    facet_wrap(~time/stepperyr, ncol=6, scales="free_y")
}

# plot weight at age time series facet wrapped by species
wageplot <- function(dat, truedat=NULL){
  ggplot(dat, aes(time/stepperyr, atoutput)) +
    geom_line(aes(colour = factor(agecl))) +
    theme_tufte() +
    theme(legend.position = "bottom") +
    xlab("model year") +
    ylab("average individual weight (g)") +
    labs(subtitle = paste0(scenario.name)) +
    facet_wrap(c("species"), scales="free_y")
}

@@

# compare with true output (all timesteps)
for(s in names(survObsBiom)){
  cat("  \n##### ",  s,"  \n")
  print(plotB(survObsBiom[[s]][[1]], omlist_ss$truetotbio_ss))
  cat("  \n")
}

# plots survey only
# for(s in names(survObsBiom)){
#   print(plotB(survObsBiom[[s]][[1]]))
# }

@@

# compare with true catch, should match
plotC(catchbio_ss, omlist_ss$truecatchbio_ss)
